\documentclass[nkz,einrichtung,usemycontact]{tucletter2019}


\ifxetex
\usepackage{polyglossia}
\setmainlanguage[spelling=new,babelshorthands=true]{english}
\else
\ifluatex
\usepackage{polyglossia}
\setmainlanguage[spelling=new,babelshorthands=true]{english}
\else
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\fi\fi


\setkomavar{subject}{Welcome - Invitation to the Orientation Period 2021}
\setkomavar{date}{31.07.2021}		% am besten immer festes Datum eintragen


\begin{document}	
\begin{letter}{%
\, \\
}

\opening{Dear Freshman,}

We would like to welcome you on behalf of all students of the faculty of mathematics. To provide you a pleasant start in your studies we – the representatives of all students of mathematics in Chemnitz – have prepared a little program for you. We would like to invite you to the\\[10pt]

\hspace*{\fill} \Large Orientation Period \hspace*{\fill} \\
\hspace*{\fill} Monday, 10/04/2021 to Friday, 10/08/2021. \normalsize \hspace*{\fill} \\[12pt]

During the Orientation Period, you can usually expect a tour through the city, the campus, student clubs and some bars, a BBQ as well as introductory courses in scientific mathematics to prepare you for your first real lectures. Due to the current situation with the Corona pandemic, it is not yet clear which of these activities can and will take place and how. We will try to hold as many events as possible in presence under the restrictions that apply at this time and hope that we can get to know each other personally during the Orientation Period. \\[10pt]


\bfseries Therefore, please keep an eye on our website\\[6pt]
\hspace*{\fill} \Large \itshape\textbf{www.tu-chemnitz.de/fsrmathe,} \upshape \normalsize \hspace*{\fill} \\[6pt]
where you will find current information and the preliminary schedule. \mdseries \\[12pt]


If you have any questions, please do not hesitate to contact us by e-mail at \itshape\textbf{fsrmathe@tu-chemnitz.de}\upshape!

Until then we wish you a pleasant summer and are looking forward to seeing you.

Yours,

Fachschaftsrat Mathematik

\end{letter}

\end{document}